Additional Tables

### 2019-08-29 notebooks/article_notebook2.Rmd
added table on prokka refs
minor changes in text

# Group listing
This table presents the groups created in the isolate selection. The "Additional Resistances" column contains how many additional antimicrobials the isolates in that group is resistant to, other than CIP and/or NAL.
```{r}
mic_data %>%
  left_join(isolate_data[,c("id","species")], by = "id") %>%
  group_by(antres, CIP, NAL, species) %>%
  count() %>%
  dplyr::rename("Additional Resistances" = antres) %>%
  ungroup() %>%
  mutate(Group = 1:n()) %>%
  dplyr::select(Group, everything()) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped","hover"))
```

@@

>>>>

# Group listing
This table presents the groups created in the isolate selection. The "Additional Resistances" column contains how many additional antimicrobials the isolates in that group is resistant to, in addition to CIP and/or NAL.
```{r}
mic_data %>%
  left_join(isolate_data[,c("id","species")], by = "id") %>%
  group_by(antres, CIP, NAL, species) %>%
  count() %>%
  dplyr::rename("Additional Resistances" = antres) %>%
  ungroup() %>%
  mutate(Group = 1:n()) %>%
  dplyr::select(Group, everything()) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped","hover"))
```

@@

# Prokka reference genomes
The genomes listed below were used as references for the Prokka annotation, and downloaded with ncbi-genome-download (https://github.com/kblin/ncbi-genome-download) with the following commands:

--refseq-category reference

--assembly-level complete

--genus "Escherichia coli" bacteria

| Accession number           |  Information                 |
|----------------------------|------------------------------|
| GCF_000005845.2_ASM584v2   | _E. coli_ K12                |
| GCF_000008865.2_ASM886v2   | _E. coli_ O157:H7 Sakai      |
| GCF_000026345.1_ASM2634v1  | _E. coli_ IAI39              |
| GCF_000183345.1_ASM18334v1 | _E. coli_ O83:H1 NRG 857C    |
| GCF_000299455.1_ASM29945v1 | _E. coli_ O104:H4 2011C-3493 |
